Intentional release of native species undermines ecological stability

### 2022-10-21 rmd/manuscript.Rmd
rmd

The reduced fitness of hatchery masu salmon may also play a role in the observed response. Like other salmonids, masu salmon exhibits a life history of "partial migration"; in our study region, the majority of individuals migrate to the ocean and spend approximately one year before spawning, although some males stay in freshwater for their entire life [@moritaLatitudinalVariationGrowth2010; @sahashiMigrationCostsDrive2013; @moritaTemperaturedependentVariationAlternative2014]. It has been shown that ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoostinpress], and such genetic effects may accumulate during the successive generations in captivity [@arakiGeneticEffectsCaptive2007]. Typically, masu salmon are reared in captivity for two to four generations. In light of the 60-year period of the extensive release program, it is conceivable that the "hatchery gene" has spread within the wild populations with measurable fitness declines. This effect may add to negative density dependence to influence community stability.

>>>>

The reduced fitness of hatchery masu salmon may also play a role in the observed response. Like other salmonids, masu salmon exhibits a life history of "partial migration"; in our study region, the majority of individuals migrate to the ocean and spend approximately one year before spawning, although some males stay in freshwater for their entire life [@moritaLatitudinalVariationGrowth2010; @sahashiMigrationCostsDrive2013; @moritaTemperaturedependentVariationAlternative2014]. It has been shown that ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoostinpress], and such genetic effects may accumulate during the successive generations in captivity [@arakiGeneticEffectsCaptive2007]. Typically, masu salmon are reared in captivity for two to four generations. In light of the 70-year period of the extensive release program, it is conceivable that the "hatchery gene" has spread within the wild populations with measurable fitness declines. This effect may add to negative density dependence to influence community stability.
